\documentclass[]{article}
\usepackage[nonumber]{cuisine}
\usepackage[]{graphicx}
%opening
\title{}
\author{}

\begin{document}

\begin{recipe}{Pork Belly Noodle Soup}{}{Makes 1 bowl}
	\ingredient[1]{lb}{Sliced Pork Belly}
	Blanch with boiling water for about 5 minutes, and discard water. 
	\ingredient[3]{oz}{Soy Sauce}
	\ingredient[2]{Tbps}{Dark Soy Sauce}
	\ingredient[1]{tsp}{Sugar}
	Place pork belly into a clean pot with soy sauces and sugar. Fill with water until the pork belly is almost covered. Simmer at 205 degrees for 1.5 hours until tender. 
	\ingredient[1]{Tbps}{Better than Bullion Roasted Chicken Base}
	\ingredient[12]{fl. oz.}{Water} 
	Combine Better than Bullion and water in a pot to make a broth, then bring to a boil. 
	\ingredient[1]{brick}{Vermicelli Noodles}
	Boil the noodles and transfer to a colander. Shock with cold water, mixing with your hands until no longer warm.
	\ingredient[3]{Sheet}{Roasted Seaweed}
	\ingredient[1]{Tbps}{Sesame Seeds}
	Slice seaweed and toss with sesame seeds.
	\ingredient[1]{Tbps}{oil}
	Slice and sear pork in a pan. Deglaze with the cooking liquid from the pork belly, and transfer into a bowl.
	\ingredient[1]{}{Scallion, sliced}
	\ingredient[1]{clump}{Cilantro}
	\ingredient[1]{Tsp}{Lime Juice (optional)}
	Place noodles on top of the cooking liquid, then place the pork on top of noodles along with scallions, cilantro, and the seaweed mix. Just before serving, pour in the broth and optionally the lime juice. 
\end{recipe}

\end{document}
