\documentclass[]{article}
\usepackage[nonumber]{cuisine}
\usepackage{gensymb}
\usepackage[margin=1in]{geometry}
\renewcommand*{\recipetitlefont}{\centering\Huge\normalfont}
%opening
\title{}
\author{}

\begin{document}
\RecipeWidths{\textwidth}{3cm}{0.5cm}{5cm} {.75cm} {.75cm}
\begin{recipe}{Butter Chicken}{}{}	
	\ingredient[140]{g}{Yogurt}
	\ingredient[10]{g}{Garam Masala (aka Curry Powder)}
	\ingredient[5]{g}{Cumin}
	\ingredient[5]{g}{Garlic Powder}
	\ingredient[5]{g}{Lime Juice}
	\ingredient[15]{g}{Salt}
	\ingredient[1.5]{lb}{Boneless Chicken Thighs}
	Whisk together yogurt and seasonings. Marinade the chicken in the mixture for 30 minutes and sear in batches. Then set aside. 
	
	\ingredient[1]{}{Yellow Onion, Diced}
	\ingredient[10]{g}{Salt}
	\ingredient[10]{g}{Pepper}
	Lower pan to medium heat and sauté until softened. 
	\ingredient[5]{g}{Garlic Powder}
	\ingredient[5]{g}{Onion Powder}
	\ingredient[15]{g}{Garam Masala}
	\ingredient[10]{g}{Paprika}
	\ingredient[2]{tsp}{ground cumin}
	\ingredient[6]{g}{Tumeric (optional)}
	\ingredient[100]{g}{Pulverized cashews}
	Add spices and sauté until spices have toasted.
	\ingredient[14]{oz}{Crushed Tomatoes}
	\ingredient[6]{oz}{water}
	Add in crushed tomatoes and water and simmer until tomatoes are soft. Using an immersion blender, blend until smooth (if you don't have an immersion blender, use a regular blender). Add in chicken and simmer until the chicken reaches 185 degrees.
	\ingredient[8]{oz}{Heavy Cream}
	Stir in Heavy cream until well incorporated. Simmer an additional 3-4 minutes.
	\ingredient[4]{Tbps}{Unsalted Butter}
	\ingredient[]{}{Salt}
	Turn off the heat and stir in unsalted butter until emulsified. Season to taste with salt. Serve with rice and cilantro.
\end{recipe}

\end{document}
