\documentclass[]{article}
\usepackage[nonumber]{cuisine}
\usepackage{gensymb}
\usepackage[margin=0.5in]{geometry}
\renewcommand*{\recipetitlefont}{\centering\Huge\normalfont}
%opening
\title{}
\author{}

\begin{document}
\RecipeWidths{\textwidth}{3cm}{0.5cm}{4cm}{1cm}{1cm}

\begin{recipe}{Black Beans}{}{}	
	\ingredient[1]{lbs}{Black Beans}
	Soak overnight. 
	\ingredient[1]{}{Onion, Diced}
	\ingredient[2]{Tbsp}{Olive Oil}
	Add olive oil and onions to pot on medium heat. Stir until softened. 
	\ingredient[6]{Cups}{Water}
	\ingredient[5]{g}{Cumin}
	\ingredient[5]{g}{Mexican Oragano}
	\ingredient[5]{g}{Garlic Powder}
	\ingredient[10]{g}{Sugar}
	\ingredient[2]{Tbsp}{Apple Cider Vinegar}
	Drain your beans, and add the drained beans to the pot. Cover with water, and add seasonings. Bring to a boil and simmer for one hour.
	\ingredient[15]{g}{Chicken base}
	Add chicken base, stir, and simmer for another hour. 
\end{recipe}

\begin{recipe}{Cilantro-Lime Rice}{}{}	
	\ingredient[180]{g}{Rice}
	\ingredient[10]{g}{Salt}
	\ingredient[1]{Tbsp}{Olive oil}
	Wash the rice. Cook the rice in a rice cooker. 
	\ingredient[1]{Tbsp}{Lime Juice}
	\ingredient[1/2]{Bunch}{Cilantro}
	Mix in lime juice and cilantro, then let rest on keep-warm. 
\end{recipe}

\begin{recipe}{Fajita Vegtables}{}{}	
	\ingredient[1 1/2]{}{Red Onion}
	\ingredient[1]{}{Bell Pepper}
	\ingredient[8]{oz}{Sliced Mushrooms}
	\ingredient[3]{Tbsp}{Olive Oil}
	\ingredient[]{}{Salt and Pepper}
	Julienne the onions and bell pepper. Add oil and vegetables to a hot pan and let sear for two minutes. Add salt and pepper, then let cook, tossing occasionally. 
\end{recipe}

\begin{recipe}{Adobe Chicken}{}{}	
	\ingredient[60]{g}{Chile Powder}
	\ingredient[15]{g}{Minced Garlic}
	\ingredient[5]{g}{Black Pepper}
	\ingredient[2]{g}{Ground Cinnamon}
	\ingredient[5]{g}{Cumin}
	\ingredient[5]{g}{Mexican Oregano}
	\ingredient[18]{g}{Apple Cider Vinegar}
	\ingredient[8]{g}{Salt}
	\ingredient[114]{fl. oz}{Water}
	Roast garlic in a pan and blend with remaining ingredients
	\ingredient[1/2]{}{Red Onion, Diced}
	\ingredient[3]{Tbsp}{Olive Oil}
	\ingredient[2]{Tbsp}{Lime Juice}
	Add additional ingredients and blend.
	\ingredient[1]{lb}{Chicken Thighs}
	Debone and flatten chicken thighs. Add marinade and chicken to a disposable bag and refrigerate for 30 minutes. 
	\ingredient[1]{Tbsp}{Vegtable Oil}
	Add oil to a cast-iron pan. Once smoking, cook chicken in batches to an internal temperature of 185 $\deg$F. 
\end{recipe}

\end{document}
